\LARGE \bf Steering a Swarm of Particles\\ Using Global Inputs and Swarm Statistics

### 2017-11-16 2017-tro-SteeringSwarmParticles/SwarmControlJournal.tex
tiny change

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{chris_portrait.jpg}}]{Chris Ertel} Chris Ertel received his B.S. in mechanical engineering from Rice University in 2010, and has since worked in industry and startups developing games, computer-aided design applications, medical telemetry systems, and other software.
Since 2013 he's collaborated with Dr. Becker on SwarmControl.net and related projects at the University of Houston Robotic Swarm Control Lab and the Rice Multi-Robot Systems Lab.

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mable.jpg}}]{Mable Wan} Mable Wan received a B.S. degree in electrical and computer engineering and a B.B.A. in entrepreneurship from the University of Houston in 2017.
Since May 2017, she has been working with Northrop Grumman Corporation in Baltimore, MD as a software engineer.
\end{IEEEbiography}

>>>>

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{chris_portrait.jpg}}]{Chris Ertel} received his B.S. in mechanical engineering from Rice University in 2010, and has since worked in industry and startups developing games, computer-aided design applications, medical telemetry systems, and other software.
Since 2013 he's collaborated with Dr. Becker on SwarmControl.net and related projects at the University of Houston Robotic Swarm Control Lab and the Rice Multi-Robot Systems Lab.

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mable.jpg}}]{Mable Wan} received a B.S. degree in electrical and computer engineering and a B.B.A. in entrepreneurship from the University of Houston in 2017.
Since May 2017, she has been working with Northrop Grumman Corporation in Baltimore, MD as a software engineer.
\end{IEEEbiography}
